Individual Differenes

### 2023-08-28 Misc/indv_diff.qmd
more slope inspections

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) ) |> 
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)),
         intErrorRank=rank((Est.Error.Intercept)),
         bandErrorRank=rank((Est.Error.bandInt)),
         nCond = n()) |> arrange(intErrorRank) |> ungroup()

@@

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    Intercept= RF_Intercept + b_Intercept,
    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
    SlopeInt=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + bandInt_RF)*condit_dummy),
    SlopeInt2=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + b_bandInt)*condit_dummy)
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt,SlopeInt2, Intercept,b_Intercept,b_bandInt) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,condit_dummy,Intercept,b_Intercept,Slope,SlopeInt,SlopeInt2,b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()

@@

full_tab <- testAvg |> select(id,condit,vx,vb,bandInt) |> 
  left_join(indvDraws |> group_by(id,bandInt) |> median_qi(estimate,Intercept,Slope), by=join_by(id,bandInt)) |>
  mutate(resid=vx-estimate) |> relocate(vx,resid,.before=estimate) |>
  mutate(across(where(is.numeric), \(x) round(x,0)))

@@

full_tab |> DT::datatable(options = list(pageLength=15))
```

@@

```{r fig.height=15, fig.width=12}
#| fig-height: 16
#| fig-width: 12
{indvDraws  |> indv_model_plot(indvSlopes, test,slopeVar=Slope, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("Slope = bandInt_RF+b_bandInt") } /
 {ggplot(indvSlopes, aes(x = Slope, color = condit)) + geom_density() } /
#gridExtra::tableGrob( indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) + 
  gt_temp(indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) +
  plot_layout(heights=unit(c(16,6,3),c('cm'))) + plot_annotation("vx ~ condit * bandInt + (1 + bandInt | id) ")
```

>>>>

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Esti")) |>
  left_join(e1Sbjs, by=join_by(id))

indv_coefs_preds <- new_data_grid |> left_join(indv_coefs,by=join_by(id,condit,condit_dummy)) |>
  mutate(
    estimate = (Estimate.Intercept) + 
      (bandInt*(Estimate.bandInt)) + 
      (condit_dummy*Estimate.conditVaried) +
      (bandInt * condit_dummy) * `Estimate.conditVaried:bandInt`)

indv_linpred <- e1_vxBMM |> linpred_draws(new_data_grid) |> 
  summarize(across(.linpred, lst(mean, sd, median), .names = "{.fn}"))

indv_epred <- e1_vxBMM |> epred_draws(new_data_grid) |>
  summarize(across(.epred, lst(mean, sd, median), .names = "{.fn}"))

indv_pred <- e1_vxBMM |> predicted_draws(new_data_grid) |>
   summarize(across(.prediction, lst(mean, sd, median), .names = "{.fn}"))

fitted(e1_vxBMM,re_formula=NA)
fitted(e1_vxBMM,re_formula=NULL) # matches epred

# |> 
#   group_by(condit) |> 
#   mutate(rank = rank(desc(Estimate.bandInt)),
#          intErrorRank=rank((Est.Error.Intercept)),
#          bandErrorRank=rank((Est.Error.bandInt)),
#          nCond = n()) |> arrange(id) |> ungroup()

@@

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    Intercept= RF_Intercept + b_Intercept,
    estimate = (b_Intercept + RF_Intercept) + 
      (bandInt*(b_bandInt+bandInt_RF)) + 
      (condit_dummy*b_conditVaried)+
      (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
    SlopeInt=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + bandInt_RF)*condit_dummy),
    SlopeInt2=bandInt_RF+b_bandInt + ((`b_conditVaried:bandInt` + b_bandInt)*condit_dummy)
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt,SlopeInt2, Intercept,b_Intercept,b_bandInt) |>
  left_join(e1Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,condit_dummy,Intercept,b_Intercept,Slope,SlopeInt,SlopeInt2,b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) #|> arrange(rankSlope)   |> ungroup()

@@

full_tab <- testAvg |> select(id,condit,vx,vb,bandInt) |> 
  left_join(indvDraws |> group_by(id,bandInt) |> median_qi(estimate,Intercept,Slope), by=join_by(id,bandInt)) |>
  mutate(resid=vx-estimate) |> relocate(vx,resid,.before=estimate) |>
  mutate(across(where(is.numeric), \(x) round(x,2)))

indvResid <- full_tab |> group_by(id,condit,bandInt) |> summarize(across(where(is.numeric), \(x) mean(x))) |>
  group_by(id,condit) |> mutate(meanResid=mean(resid)) |>
  arrange(meanResid)

@@

full_tab |> DT::datatable(options = list(pageLength=10))
```

@@

```{r fig.height=15, fig.width=12}
#| fig-height: 16
#| fig-width: 12
{indvDraws  |> indv_model_plot(indvSlopes, test,slopeVar=Slope, rank_variable=Slope,n_sbj=n_sbj,"max") + 
     ggtitle("Slope = bandInt_RF+b_bandInt") } /
 {ggplot(indvSlopes, aes(x = Slope, color = condit)) + geom_density() } /
 gridExtra::tableGrob( indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) + 
  #gt_temp(indvSlopes |> group_by(condit) |> summarise(Mean=mean(Slope),Sd=sd(Slope)) ) +
  plot_layout(heights=unit(c(16,6,3),c('cm'))) + plot_annotation("vx ~ condit * bandInt + (1 + bandInt | id) ")
```
